Recruiting Chapter

### 2020-12-18 manuscript.Rmd
add figures to manuscript

---
title: "Recruiting Chapter"
author: "Ozan Jaquette"
bibliography: ./other/burd_recruiting_chapter.bib
output: 
  bookdown::pdf_document2:
    toc: FALSE
csl: ./other/apa.csl
urlcolor: blue
header-includes:
      - \usepackage{pdflscape}
      - \usepackage{geometry}
---

@@

Tables/Figures X and X show simple counts and descriptive staitistics of off-campus recruiting visits by colleges and universities in our sample. TEXT BRIEFLY DESCRIBING FINDINGS FROM DESCRIPTIVE TABLES.... Table/Figure X demonstrates the disproportionate number of visits to private high schools. The goal of this chapter is to investigate off-campus recruiting visits to private high schools. Which types of private high schools receive visits from which types of colleges and universities? Additionally, to what extent were visits a college/university to a private high school more likely if the two organizations were similar to one another on key characteristics? Our analyses focus on the characteristics of academic reputation, geographic region, religious affiliation, and racial composition. WHAT TO SHOW IN TABLES/FIGURES:
<!--
- Table/figure of number of visits by visit type and in/out-of-state
- Table/figure showing disproportionate number of visits to private high schools.
-->

@@

```{r, echo=FALSE}
pct_budget <- data.frame(
  activity = c("Travel","Student search (purchased lists)","Prospective student communications","Events","Recruitment publications","Web services and digital advertising","Traditional advertising","International recruitment","Transfer recruitment","Other"),
  private = c(17,14,13,12,11,11,6,5,4,8),
  public = c(16,12,17,11,15,13,6,3,4,3)
)

@@

```{r, hs-print-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_privu.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-name,-closeness), caption = 'The 20 most central private high schools with respect to visits from private colleges and universities') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, hs-table-privu-agg, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_agg_privu.RDS')

knitr::kable(df, caption = 'characteristics of high schools by degree band, private colleges and universities') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

```{r, hs-print-pubu, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_pubu.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-name,-closeness), caption = 'The 20 most central private high schools with respect to visits from public research universities') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, hs-table-pubu-agg, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_agg_pubu.RDS')

knitr::kable(df, caption = 'characteristics of high schools by degree band, public research universities') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

```{r, hs-print-both, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_both.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-name,-closeness), caption = 'most central private high schools, public and private colleges and universities') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, hs-table-both-agg, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_agg_both.RDS')

knitr::kable(df, caption = 'characteristics of high schools by degree band, public and private colleges and universities') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

```{r em-funnel, echo = FALSE, fig.cap = "The enrollment funnel"}
knitr::include_graphics('assets/images/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png)
```

@@

\newgeometry{margin=0cm}

@@

```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_2mode_all_region.pdf')

@@

```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-privu"}
knitr::include_graphics('assets/figures/plot_1mode_privu.pdf')
```

```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE}
#df <-readRDS(file.path('.', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS')))
#df %>% glimpse()

plot_characteristic <- function(df, type, characteristic) {
  sub_df <- df %>% select(univ_name, characteristic) %>%
    gather(key, value, characteristic) %>%
    mutate(value = parse_number(value))

  # colors <- sub_df$color[order(sub_df$University)]
  univ_order <- (df %>% arrange(desc(cluster), univ_name))$univ_name
  #univ_order <- (df %>% arrange(desc(Cluster), Type, as.numeric(Rank), University))$University
  sub_df$univ_name <- factor(sub_df$univ_name, levels = rev(univ_order))
  #sub_df$univ_name

  ggplot(sub_df, aes(fill = key, y = value, x = univ_name)) + 
    geom_bar(stat='identity', position = position_fill(reverse = TRUE)) +
    ggtitle('Title') +
    xlab('') + ylab('') +
    labs(fill = type) +
    scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
    theme(legend.position = 'top',
          legend.title = element_text(size = 6, face = 'bold'),
          legend.text = element_text(size = 6),
          legend.margin = margin(0, 0, 0, 0),
          legend.box.margin = margin(0, 0, -5, -30),
          legend.key.size = unit(0.3, 'cm'),
          panel.background = element_blank(),
          axis.ticks.y = element_blank(),
          # axis.text.y = element_text(color = rep(c('red', 'green', 'blue', 'yellow', 'black'), 5)),
          text = element_text(size = 8),
          plot.title = element_text(color = 'white')) +
    coord_flip()
}

type_vec <- c('privu', 'pubu', 'pubu_outst', 'all','all_pubu_outst')

@@

  a <- plot_characteristic(ego_df, 'Region', c('northeast', 'midwest', 'south', 'west'))
  b <- plot_characteristic(ego_df, 'Religion', c('catholic', 'christian', 'nonsectarian', 'other'))
  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))

  grid.arrange(a, b, c, d, nrow=2, ncol=2)
  dev.off()

  # Need to use print() for ggplot inside loop in order for it to appear
  # https://stackoverflow.com/a/15678596/6373540
  #print(a)
  #print(b)
  #print(c)
  #print(d)
}
```

@@

\newgeometry{margin=0cm}

@@

```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by private colleges and universities"}
knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
```

@@

```{r villanova-religion, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Villanova University, with religious affiliation"}
knitr::include_graphics('assets/figures/villanova_religion.pdf')
```

```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Emory University, with geographic region"}
knitr::include_graphics('assets/figures/emory_region.pdf')
```

```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-pubu"}
knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
```

```{r plot-1mode-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-pubu out-of-state visits only", eval = FALSE}
knitr::include_graphics('assets/figures/plot_1mode_pubu_outst.pdf')
```

@@

```{r ego-network-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by public research universities"}
knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
```

@@

```{r plot-1mode-all, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-all", include= FALSE, eval = FALSE}
knitr::include_graphics('assets/figures/plot_1mode_all.pdf')
```

```{r plot-1mode-all-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-all, out-of-state visits only for public universities"}
knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
```

@@

```{r ego-network-figure-all-pubu-outst, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by public and private colleges and universities, out-of-state visits only for public universities"}
knitr::include_graphics('assets/figures/ego_network_figure_all_pubu_outst.pdf')
#out.width="1.1\\linewidth", 
```

>>>>

---
title: "Recruiting Chapter"
author: "Ozan Jaquette"
bibliography: ./other/burd_recruiting_chapter.bib
output: 
  bookdown::pdf_document2:
    toc: FALSE
csl: ./other/apa.csl
urlcolor: blue
header-includes:
      - \usepackage{pdflscape}
      - \usepackage{geometry}
      - \usepackage{floatrow}
      - \floatsetup{capposition=top}
---

@@

Figures \@ref(fig:event-count-figure-privu) and \@ref(fig:event-count-figure-pubu) show simple counts and descriptive statistics of off-campus recruiting visits by colleges and universities in our sample. TEXT BRIEFLY DESCRIBING FINDINGS FROM DESCRIPTIVE TABLES.... Table/Figure X demonstrates the disproportionate number of visits to private high schools. The goal of this chapter is to investigate off-campus recruiting visits to private high schools. Which types of private high schools receive visits from which types of colleges and universities? Additionally, to what extent were visits a college/university to a private high school more likely if the two organizations were similar to one another on key characteristics? Our analyses focus on the characteristics of academic reputation, geographic region, religious affiliation, and racial composition. WHAT TO SHOW IN TABLES/FIGURES:
<!--
- Table/figure of number of visits by visit type and in/out-of-state
- Table/figure showing disproportionate number of visits to private high schools.
-->

@@

```{r ug-recruit-budget, echo=FALSE}
pct_budget <- data.frame(
  activity = c("Travel","Student search (purchased lists)","Prospective student communications","Events","Recruitment publications","Web services and digital advertising","Traditional advertising","International recruitment","Transfer recruitment","Other"),
  private = c(17,14,13,12,11,11,6,5,4,8),
  public = c(16,12,17,11,15,13,6,3,4,3)
)

@@

```{r hs-print-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_privu.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-name,-closeness), caption = 'Top 20 most central private HS visited by private institutions') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r hs-table-privu-agg, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_agg_privu.RDS')

knitr::kable(df, caption = 'Characteristics of private HS visited by private institutions, by degree band') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

```{r hs-print-pubu, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_pubu.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-name,-closeness), caption = 'Top 20 most central private HS visited by public institutions') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r hs-table-pubu-agg, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_agg_pubu.RDS')

knitr::kable(df, caption = 'Characteristics of private HS visited by public institutions, by degree band') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

```{r hs-print-both, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_both.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-name,-closeness), caption = 'Top 20 most central private HS visited by all institutions') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r hs-table-both-agg, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_agg_both.RDS')

knitr::kable(df, caption = 'Characteristics of private HS visited by all institutions, by degree band') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

```{r em-funnel, echo = FALSE, fig.align = 'center', fig.cap = "The enrollment funnel", out.width = "70%"}
knitr::include_graphics('assets/images/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png)
```

```{r event-count-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for private institutions"}
knitr::include_graphics('assets/figures/plot_event_count_privu.pdf')
```

```{r event-count-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for public institutions"}
knitr::include_graphics('assets/figures/plot_event_count_pubu.pdf')
```

@@

```{r privhs-universe, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of universe of private HS and private HS that received at least 1 visit from sample institutions, unweighted and weighted by 12th grade enrollment"}
knitr::include_graphics('assets/figures/plot_pss_universe.pdf')
```

\begin{center}
* \textit{Universe of private HS (N=3673), private HS visited by sample institutions (N=1738); Universe of private HS is defined as any private schools that enrolls at least ten grade 12 students and is not a special education school, an alternative school, an early childhood center, or an independent school.}
\end{center}

\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}

@@

```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "2-mode network for all institutions, colored by geographic region"}
knitr::include_graphics('assets/figures/plot_2mode_all_region.pdf')

@@

```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for private institutions, colored by cluster"}
knitr::include_graphics('assets/figures/plot_1mode_privu.pdf')
```

```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE}
# ggplot's default color palette
# library(scales)
# show_col(hue_pal()(4))

plot_characteristic <- function(df, type, characteristic, label_text, visit_count = FALSE) {
  if (visit_count) {
    df <- df %>% mutate(univ_name = str_c(univ_name, ' (N=', total, ')'))
  }

  ordered_df <- df %>% arrange(desc(cluster), univ_name)
  univ_order <- ordered_df$univ_name
  cluster_face <- map_chr(ordered_df$cluster, function(x) if_else(as.numeric(x) %% 2 == 0, 'bold', 'plain'))

  sub_df <- df %>% select(univ_name, all_of(characteristic)) %>%
    gather(key, value, characteristic) %>%
    mutate(value = parse_number(value))

  sub_df$univ_name <- factor(sub_df$univ_name, levels = rev(univ_order))
  sub_df$key <- factor(sub_df$key, levels = characteristic)

  ggplot(sub_df, aes(fill = key, y = value, x = univ_name)) + 
    geom_bar(stat='identity', position = position_fill(reverse = TRUE)) +
    ggtitle('Title') +
    xlab('') + ylab('') +
    labs(fill = type) +
    scale_fill_manual(labels = label_text, values = c('#F8766D', '#7CAE00', '#00BFC4', '#C77CFF')) +
    scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
    theme(legend.position = 'top',
          legend.title = element_text(size = 6, face = 'bold'),
          legend.text = element_text(size = 6),
          legend.margin = margin(0, 0, 0, 0),
          legend.box.margin = margin(0, 0, -5, -30),
          legend.key.size = unit(0.3, 'cm'),
          panel.background = element_blank(),
          axis.ticks.y = element_blank(),
          axis.text.y = element_text(face = rev(cluster_face)),
          text = element_text(size = 8),
          plot.title = element_text(color = 'white')) +
    coord_flip()
}

type_vec <- c('privu', 'pubu', 'pubu_outst', 'all', 'all_pubu_outst')

@@

  a <- plot_characteristic(ego_df, 'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE)
  b <- plot_characteristic(ego_df, 'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'))
  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'), c('<10%', '10-25%', '25-50%', '50%+'), visit_count = TRUE)
  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'))

  grid.arrange(a, b, c, d, nrow=2, ncol=2, widths=c(1, 0.92))
  dev.off()

  # Need to use print() for ggplot inside loop in order for it to appear
  # https://stackoverflow.com/a/15678596/6373540
  # print(a)
  # print(b)
  # print(c)
  # print(d)
}
```

@@

\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}

@@

```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by private institutions"}
knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
```

\begin{center}
* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
\end{center}

@@

```{r villanova-religion, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Villanova University, colored by religious affiliation"}
knitr::include_graphics('assets/figures/villanova_religion.pdf')
```

```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Emory University, colored by geographic region"}
knitr::include_graphics('assets/figures/emory_region.pdf')
```

```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for public institutions, colored by cluster"}
knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
```

```{r plot-1mode-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for public institutions and out-of-state visits only, colored by cluster", eval = FALSE}
knitr::include_graphics('assets/figures/plot_1mode_pubu_outst.pdf')
```

@@

```{r ego-network-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by public institutions"}
knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
```

\begin{center}
* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
\end{center}

@@

```{r plot-1mode-all, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for all institutions, colored by cluster", include= FALSE, eval = FALSE}
knitr::include_graphics('assets/figures/plot_1mode_all.pdf')
```

```{r plot-1mode-all-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for all institutions, out-of-state visits only for public universities, colored by cluster"}
knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
```

@@

```{r ego-network-figure-all-pubu-outst, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by all institutions, out-of-state visits only for public universities"}
knitr::include_graphics('assets/figures/ego_network_figure_all_pubu_outst.pdf')
#out.width="1.1\\linewidth", 
```

\begin{center}
* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
\end{center}
